New Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations

### 2020-01-01 _other/tikz/tree/fs_tikz_gametree.tex
tikz tree, vim set up, other setup updates

>>>>

\section{Grow Three to the Right, Discrete and Continuous Muliple}

There are three choices, choose consumption share first, which also means the residual goes to overall investment share.

\begin{enumerate}
  \item \textbf{continous}, choose consumption, or aggregate investment, rightward bend span, three node, center longer to match bend
  \item \textbf{continous}, choose investment in capital, type 1 asset, residual goes to type two asset, rightward span, three node, center longer to match bend
  \item \textbf{discrete}, within type 2 asset, choose a achieve the desired level of type two, rightward, five nodes, equi-distance
\end{enumerate}

\subsection{Nodes Only}

When developing trees, to simply the problem, first just draw nodes and branches, no text, no benidng, no coloring.

\def\famm{5mm}
\begin{center}
\begin{tikzpicture}[scale=1.5,font=\footnotesize]W
\tikzstyle{level 1}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 2}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 3}=[level distance=\famm,sibling distance=\famm]
% B Level 1 point
\node(0)[solid node,label=left:{$P1$}]{}
[grow=right]
child
child{
    [grow=right]
    child
    child{
        [grow=right]
        child
        child
        child
        child
        child
        }
    child
    }
child;
\end{tikzpicture}
\end{center}

### 2020-01-01 nontex/install/git/fs_git_setup.Rmd
tikz tree, vim set up, other setup updates

```{bash}
# Initialize Repositories, do these one by one first
cd ~/fanwangecon.github.io
git pull github master
cd ~/PyFan
git pull github master
cd ~/Tex4Econ
git pull github master
cd ~/R4Econ
git pull github master
cd ~/M4Econ
git pull github master
cd ~/Py4Econ
git pull github master
cd ~/Teaching
git pull github master
```

@@

```{bash}
# Initialize Repositories, do these one by one first
cd ~/fanwangecon.github.io
git push -u github master
cd ~/PyFan
git push -u github master
cd ~/Tex4Econ
git push -u github master
cd ~/R4Econ
git push -u github master
cd ~/M4Econ
git push -u github master
cd ~/Py4Econ
git push -u github master
cd ~/Teaching
git push -u github master
```

>>>>

```{bash}
# Pull from Repositories, do these one by one first
cd ~/fanwangecon.github.io
git pull github master
cd ~/PyFan
git pull github master
cd ~/Tex4Econ
git pull github master
cd ~/R4Econ
git pull github master
cd ~/M4Econ
git pull github master
cd ~/Py4Econ
git pull github master
cd ~/Teaching
git pull github master
```

@@

```{bash}
# Push to Repositories, do these one by one first
cd ~/fanwangecon.github.io
git push -u github master
cd ~/PyFan
git push -u github master
cd ~/Tex4Econ
git push -u github master
cd ~/R4Econ
git push -u github master
cd ~/M4Econ
git push -u github master
cd ~/Py4Econ
git push -u github master
cd ~/Teaching
git push -u github master
```

### 2020-01-01 nontex/install/linux/fn_vim.Rmd
tikz tree, vim set up, other setup updates

## Install Neovim in Conda (Windows)

@@

Create init.vim file:

@@

" For LimeLight
" Color name (:help cterm-colors) or ANSI code
let g:limelight_conceal_ctermfg = 'gray'
let g:limelight_conceal_ctermfg = 240
" Color name (:help gui-colors) or RGB color
let g:limelight_conceal_guifg = 'DarkGray'
let g:limelight_conceal_guifg = '#777777'
" if Limelight should highlight line rather than paragraph
" let g:limelight_bop = '^.*$'
" let g:limelight_eop = '\n'
let g:limelight_paragraph_span = 0

@@

"""""""""""""""""""""""""""""""""""""""""""""""""
" Markdown **, * etc settings
"""""""""""""""""""""""""""""""""""""""""""""""""
" set concealcursor=n
" set conceallevel=3
" hi Asterisks NONE
" hi AsteriskBold  cterm=bold gui=bold
" syn match Asterisks contained "**" conceal
" syn match AsteriskBold "\\\@<!\*\*[^"*|]\+\*\*" contains=Asterisks
autocmd VimEnter * highlight Normal ctermbg=black
" ctermfg=grey

@@

>>>>

## Install Neovim in Windows

Install and access neovim all from windows powershell. Type in *powershell* in regular command prompt for example.

### Install Neovim and Vim-Plug in Windows

@@

### Set up init.vim File in Windows

Inside powershell, create init.vim file:

@@

" For LimeLight
" Color name (:help cterm-colors) or ANSI code
let g:limelight_conceal_ctermfg = 'gray'
let g:limelight_conceal_ctermfg = 240
" Color name (:help gui-colors) or RGB color
let g:limelight_conceal_guifg = 'DarkGray'
let g:limelight_conceal_guifg = '#777777'
" if Limelight should highlight line rather than paragraph
let g:limelight_bop = '^.*$'
" let g:limelight_eop = '\n'
let g:limelight_paragraph_span = 0

@@

"""""""""""""""""""""""""""""""""""""""""""""""""
" Markdown **, * etc settings
"""""""""""""""""""""""""""""""""""""""""""""""""
" set concealcursor=n
" set conceallevel=3
" hi Asterisks NONE
" hi AsteriskBold  cterm=bold gui=bold
" syn match Asterisks contained "**" conceal
" syn match AsteriskBold "\\\@<!\*\*[^"*|]\+\*\*" contains=Asterisks
" autocmd VimEnter * highlight Normal ctermbg=black
" ctermfg=grey

@@

### Full Screen Vim Window in Windows

It is nice to have full screen, no distraction work experience. To set command prompt to full screen (to get rid of scrolling bar on the right in full screen), use windows command prompt which allows for full screen, right click on window top border, choose property, then choose layout, then set height and width of window size and buffer size to be the same. This will allow for full screen experience.

### 2020-01-01 nontex/install/windows/fn_installations.Rmd
tikz tree, vim set up, other setup updates

```{bash}
# Once atom is installed, can use apm to install packages
apm install hydrogen
apm install project-manager
# Inside Conda open up atom
atom
# open multiple projects from atom at the same time, after repos synced
atom ~/fanwangecon.github.io ~/Pyfan ~/Teaching ~/Tex4Econ ~/R4Econ ~/M4Econ ~/Py4Econ
# open up any py from from within, try 1+1, does it work?
# also use script, try ctrl + shift + b, run whole file (not hydrogen)
```

@@

1. latex compiler: pdflatex, etc
2. tex distributions: MikTex, texlive
    + these folders, once various packages are installed, could be very large, many GB
3. latex packages from distributions
3. editor (gui): Atom, texStudio, etc

@@

## Development Programs

- [pycharm](https://www.jetbrains.com/pycharm/)

>>>>

```{bash}
# Once atom is installed, can use apm to install packages
apm install hydrogen
apm install project-manager
apm install sublime-style-column-selection

# Inside Conda open up atom
atom

# open multiple projects from atom at the same time, after repos synced
atom ~/fanwangecon.github.io ~/Pyfan ~/Teaching ~/Tex4Econ ~/R4Econ ~/M4Econ ~/Py4Econ
# open up any py from from within, try 1+1, does it work?
# also use script, try ctrl + shift + b, run whole file (not hydrogen)
```

@@

1. latex compiler: pdflatex, etc
2. tex distributions: MikTex, texlive
    + these folders, once various packages are installed, could be very large, many GB
3. latex packages from distributions
3. editor (gui): Atom, Sublime text, texStudio, etc

@@

## Editors

In addition to Atom.

### Notepad++

[Notepad++](https://notepad-plus-plus.org/downloads/v7.8.2/). Many old projects have xml folder structures for Notepad++.

- Silently update file changes made in other editors: Settings, Preferences, MISC., File Status Auto Detection, Update Silently.
### Sublime

[Sublime](https://www.sublimetext.com/3)

there are some issues with atom. When a file is edited inside Vim, when changes are saved, a [temp file is created in atom](https://github.com/atom/atom/issues/17186). Sublime would, however, still show the file with the changes. This makes dual screen editing very difficult. Sublime text is used for this situation.

*Sublime Setup*:

- [r and rmd setup](https://weibeld.net/r/rmd_sublime_package.html)

### PyCharm

[pycharm](https://www.)jetbrains.com/pycharm/)
